DAG test

### 2022-11-18 DAG.Rmd
Commit

  u~yk/(bd_nfc_k+equip_nfc_k)

@@

```{r, fig.width= 15, fig.height=10}
library(ggraph)
library(tidygraph)
tb_graph %N>% 
  filter(!node_is_isolated()) %>%
  ggraph(layout = 'stress') + 
  geom_edge_fan(arrow = arrow(angle = 30, length = unit(0.4, 'cm'),type = 'closed'), alpha = 0.4) + 
  geom_node_point(aes(col = cyclical, size = centrality_eigen(directed = TRUE))) +
  geom_node_text(aes(label = name, size = 0.5)) + 
  theme_graph() +
  theme(legend.position = "bottom") 
```

>>>>

  u~yk/(bd_nfc_k+equip_nfc_k),

   pc ~ TSDELTALOG(TSLAG(pc,1)) + TSDELTALOG(TSLAG(pc,2))+ TSDELTALOG(TSLAG(pc,3)) + TSDELTALOG(TSLAG(pc,4)) 
  + TSDELTALOG(wage)+ TSDELTALOG(pm) + TSDELTALOG(TSLAG(pm,2)) + LOG(TSLAG(pc,1)) + LOG(TSLAG(wage,1))
  + LOG(TSLAG(prod,1)) + LOG(TSLAG(pm,1)),

  rer ~ pc*xr/pf,

   i_equip_nfc_k ~  TSDELTALOG(TSLAG(i_equip_nfc_k,1)/TSLAG(equip_nfc_k,2)) +
    LOG(TSLAG(i_equip_nfc_k,1)/TSLAG(equip_nfc_k,2)) +
     LOG(TSLAG(ps,1)) +
    LOG(TSLAG(u,1)) +
    TSDELTALOG(tobinq) +
    LOG(TSLAG(tobinq,1))

@@

```{r, fig.width= 15, fig.height=10}
library(ggraph)
library(tidygraph)
tb_graph %N>% 
  filter(!node_is_isolated()) %>%
  ggraph(layout = 'stress') + 
  geom_edge_fan(strength=3 ,arrow = arrow(angle = 30, length = unit(0.35, 'cm'),type = 'closed'), alpha = 0.4) + 
  geom_node_point(aes(col = cyclical, size = 3)) +
  geom_node_text(aes(label = name, size = 3),nudge_y=0) + 
  theme_graph() +
  theme(legend.position = "bottom") 
```
